R Tools for Obspack, Footprints and Receptors (rtorf)

### 2024-07-08 README.Rmd
web page

![GitHub commit
activity](https://img.shields.io/github/commit-activity/y/noaa-gml/rtorf)

[![R build
status](https://github.com/ibarraespinosa/rtorf/workflows/draft-pdf/badge.svg)](https://github.com/ibarraespinosa/rtorf/actions)

[![R-CMD-check](https://github.com/noaa-gml/torf/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/noaa-gml/torf/actions/workflows/R-CMD-check.yaml)

>>>>

 <!-- badges: start -->

![GitHub commit
activity](https://img.shields.io/github/commit-activity/y/noaa-gml/rtorf)
  [![R-CMD-check](https://github.com/noaa-gml/rtorf/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/noaa-gml/rtorf/actions/workflows/R-CMD-check.yaml)
  <!-- badges: end -->
